### 2013-11-01 inst/examples/policycosts/writeup.Rmd
more reps

```{r reduction}
reduction <- 0.5 
```

@@

Find the value of `c2` that brings each penalty closest to 75% of the cost-free adjustment value:

@@

reps <- 1:10
names(reps) = paste("rep", 1:10, sep="_")
sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))

@@

# Profit when accounting for penalty when present
optimal_cost <- dt[, sum(profit_fishing), by=penalty_fn ] 
# Profit when ignoring penalty when present
ignore_when_present <- dt[, sum(profit_fishing_alt), by=penalty_fn] 
# Profit when assuming penalty when it is absent
assume_when_absent <- dt_free[, sum(profit_fishing), by=penalty_fn]
# Profit when ignoring penalty when it is absent
optimal_free <- dt_free[, sum(profit_fishing_alt), by=penalty_fn]

# Normalize by the optimal 
ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1

@@

@@

>>>>

```{r reduction}
reduction <- 0.25 
```

@@

Find the value of `c2` that brings each penalty closest to `r reduction*100`% of the cost-free adjustment value:

@@

reps <- 1:100
names(reps) = paste("rep", 1:10, sep="_")
sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))

@@

# Profit when accounting for penalty when present
optimal_cost <- dt[, sum(profit_fishing - policy_cost), by=penalty_fn ] 
# Profit when ignoring penalty when present
ignore_when_present <- dt[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn] 
# Profit when assuming penalty when it is absent
assume_when_absent <- dt_free[, sum(profit_fishing - policy_cost), by=penalty_fn]
# Profit when ignoring penalty when it is absent
optimal_free <- dt_free[, sum(profit_fishing_alt - policy_cost_alt), by=penalty_fn]

# Normalize by the optimal 
#ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
#assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1

@@

print_npv # theoretically acheivable profits under these costs
optimal_cost$V1/optimal_free$V1 # actually realized

@@

```{r error_costs_table} 
print(xtable(error_costs), type="html")
#pandoc.table(print_npv)
```
